---
title: Retrieve Content Information for R, Python, and Quarto versions
execute: 
  eval: false
---

This recipe yields content information grouped by the versions of R, Python, or Quarto that were used to create that content. 

## Requirements

- CONNECT_SERVER environment variable
- CONNECT_API_KEY environment variable for an administrator or publisher^[the publisher must have access to the content item to retrieve usage statistics]
- Content guid for content of interest


## Method 

Connect records content visits (or "hits") for all content types. These may be user visits to the content or programmatic requests to content or APIs hosted on Connect. 









::: {.callout-note}

::: 

This recipe provides methods for:

1. Retrieving overall historical content usage
2. Identifying usage by user
3. Deploying a sample Quarto dashboard using these methods 


### Setup

Install the required packages.

::: {.panel-tabset group="language"}
## Python

We strongly recommend the use of virtual environments to manage project-level dependencies. The code below uses `venv` for this purpose.

```{.bash}
# In your project directory

# create virtual environment and activate it
python -m venv .venv && source .venv/bin/activate

# upgrade pip, setuptools, and install wheel
python -m pip install -U pip setuptools wheel

# install the `posit-sdk` package
pip install posit-sdk
```

## R

We strongly recommend the use of virtual environments to manage project-level dependencies. The code below uses `renv` for this purpose.

```{r}
# In your project directory

# install `renv` package
install.packages(renv)

# initialize the project-level environment
renv::init()

# install required packages
install.packages(c("connectapi", "tidyverse"))

```


:::


### Retrieve historical XXXX data

The code samples below will yield content XXXX data as a data frame.

:::{.panel-tabset group="language"}

## Python 

```{python}

```



## R

```{r}
### Load required packages
library(connectapi)
library(tidyverse)

### User-defined inputs
# 1. specify the guid for the content
# content_guid <- "INSERT_CONTENT_GUID" 

# # 2. Specify timeframe for the report. Default is 30 days prior to today
# as_of_date <- lubridate::today()
# days_back <- 30

# report_from <- as_of_date - lubridate::ddays(days_back)

### Establish connection to Connect server
# Note `connectapi::connect` will automatically detect the environment variables CONNECT_SERVER and CONNECT_API_KEY. They do not need to be specified as arguments to this function, however, if these environment variables are not set, the code will fail
client <- connectapi::connect()

### Determine if 
# Retrieve content details
content_info <- connectapi::get_content(client, limit = Inf)

# Retain only MAJOR.MINOR version components.
major_minor  <-  function(versions) {
  sapply(versions, function(version) {
    if (is.na(version) || version == "") {
      NA
    } else {
      parts <- strsplit(version, ".", fixed = TRUE)[[1]]
      paste(parts[1:2], collapse = ".")
    }
  })
}

version_info <- content_info |> 
  mutate(
    python_version = major_minor(py_version),
    r_version = major_minor(r_version),
    quarto_version = major_minor(quarto_version)
  ) |> 
  select(guid, title, created_time, last_deployed_time, 
         app_mode, r_version, python_version, quarto_version, owner, owner_guid, id, app_role, content_url, dashboard_url)
  
# number of items by version

version_table <- version_info |> 
  select(python_version, r_version, quarto_version) |> 
  group_by(python_version, r_version, quarto_version) |> 
  summarise(N = n()) |> 
  arrange(desc(python_version), desc(r_version), desc(quarto_version)) |> 
  ungroup() 

version_table()




```

Sample output:
```

```

The output above can be plotted for a historical perspective on content usage. An example is included in the Quarto dashboard code at the end of this recipe.

:::

### Identifying usage by user

The code samples below will yield by-user content usage data as a data frame. 

::: {.panel-tabset group="language"}

## Python


## R

```{r}
### Get user details to cross reference `user_guid` with usernames
all_users <- connectapi::get_users(client, limit = Inf)

### Join user data with usage data
by_user_usage <- usage |>
                  select(user_guid, day) |> 
                  group_by(user_guid) |> 
                  # add a column for total visits/hits by that user
                  mutate(total_visits = n()) |> 
                  ungroup() |> 
                  group_by(user_guid, day) |> 
                  # add a column for visits/hits by that user on a particular day
                  mutate(daily_visits = n()) |> 
                  ungroup() |> 
                  # cross reference with user data to bring in usernames
                  left_join(all_users, by = c(user_guid = "guid")) |> 
                  # if content was accessed anonymously, the user_guid will be NA. Replace these with "anonymous"
                  mutate(username = coalesce(username, "anonymous")) |> 
                  select(username, day, total_visits, daily_visits) |> 
                  distinct() |> 
                  arrange(desc(total_visits))

### View by-user usage data as a data frame
by_user_usage
```

Sample output:
```
# A tibble: 9 × 4
  username       day                 total_visits daily_visits
  <chr>          <dttm>                     <int>        <int>
1 lisa           2024-03-19 00:00:00            4            2
2 lisa           2024-03-20 00:00:00            4            2
3 daniel         2024-03-08 00:00:00            2            1
4 daniel         2024-03-12 00:00:00            2            1
5 andrie         2024-03-20 00:00:00            2            1
6 andrie         2024-03-21 00:00:00            2            1
7 sam            2024-03-14 00:00:00            1            1
8 katie          2024-03-25 00:00:00            1            1
9 connor         2024-03-26 00:00:00            1            1
```

The output above can be plotted for a historical perspective on content usage. An example is included in the Quarto dashboard code at the end of this recipe.

:::


## Deploy a sample Quarto dashboard with these metrics

The Quarto document below builds visualizations around the data frames retrieved above. This can be deployed in your own environment, or customized to your needs.

<!-- TODO: Add github repo and manifest.json link -->



::: {.panel-tabset group="language"}
## Python

Tab content

## R

<!-- TODO: Make this embed work -->

{{ < include _usage-dashboard.qmd > }}

:::