---
title: Identify all content owned by a user
execute:
  eval: false
---

## Description

This recipe identifies all content owned by a specified user.

This may be useful for auditing purposes, changing content ownership when an employee leaves the company, or creating a list of content that would be the input for another recipe in this guide.

## Output

This recipe generates both a raw data frame identifying all content owned by a specified user, as well as a formatted table suitable for incorporating into a report or application.

## Workflow

1. The username of the user whose content you want to identify.

This recipe then does the following:

1. Retrieves all content owned by the specified user.
2. Formats the output into a table for easier readability.

## Recipe

### Dataframe of content owned by user

::: {.panel-tabset group="language"}
## Python

```{python}
from posit import connect
import polars as pl


#### User-defined inputs ####
# 1. specify the username for the user of interest
username = "SPECIFY USERNAME"
###########################

client = connect.Client()

# Get user's `guid` from specified username
user_guid = client.users.find_one(prefix = username).guid
#TODO: change method to `client.users.find_one(prefix=username).content.find()` per https://github.com/posit-dev/posit-sdk-py/issues/180
# Get list of content owned by specified user
content = pl.DataFrame(client.content.find(owner_guid=user_guid))
content
```

### Example output

```
shape: (3, 45)
            guid	           name	            title	     description	access_type	connection_timeout	read_timeout	init_timeout	idle_timeout	max_processes	min_processes	max_conns_per_process	load_factor	memory_request	memory_limit	cpu_request	cpu_limit	amd_gpu_limit	nvidia_gpu_limit	service_account_name	default_image_name	    created_time	last_deployed_time	bundle_id	       app_mode	content_category	parameterized	cluster_name	image_name	r_version	py_version	quarto_version	r_environment_management	default_r_environment_management	py_environment_management	default_py_environment_management	run_as	run_as_current_user	      owner_guid	     content_url	   dashboard_url	app_role	  id	                                                                                                                                  tags	                                                                       owner
             str	            str	              str	             str	       str	              null	        null	        null	        null           	 null	         null	                 null	       null	          null	        null	       null	     null	         null	            null	                null	              null	             str	               str	      str	            str	             str	         bool	         str	      null	     null	       str	           str	                    null	                            null	                     bool	                             null	  null	               bool	             str	             str	             str	     str	 str	                                                                                                                       list[struct[5]]	                                                                   struct[4]
"f55cdaed-c13e-…	"cgrndhmmpnsgp"	"Literate Progr…	"An open-source…	     "all"	              null	        null	        null	        null           	 null	         null	                 null	       null	          null	        null	       null	     null	         null	            null	                null	              null	"2024-04-02T17:…	  "2024-04-02T17:…	     "11"	"quarto-static"	              ""	        false	     "Local"	      null	     null	  "3.11.6"	     "1.4.549"	                    null	                            null	                     true	                             null	  null	              false	"010b18bf-96b9-…	"https://wonder…	"https://wonder…	 "owner"	"11"	 [{"7","Python","1","2024-04-02T17:52:08Z","2024-04-02T17:52:08Z"}, {"12","Quarto","7","2024-04-02T17:55:25Z","2024-04-02T17:55:25Z"}]	{"010b18bf-96b9-499f-bb0f-7519a22ca870","publisher1","Publisher1","Account"}
"1c5278e5-a654-…	"cjbxgjmdaqodv"	"Loan Risk Pred…	"An API serving…	     "all"	              null	        null	        null	        null           	 null	         null	                 null	       null	          null	        null	       null	     null	         null	            null	                null	              null	"2024-04-02T17:…	  "2024-04-02T17:…	     "10"	"python-fastapi…              ""	        false	     "Local"	      null	     null	  "3.11.6"	          null	                    null	                            null	                     true	                             null	  null	              false	"010b18bf-96b9-…	"https://wonder…	"https://wonder…	 "owner"	"10"	[{"7","Python","1","2024-04-02T17:52:08Z","2024-04-02T17:52:08Z"}, {"11","FastAPI","7","2024-04-02T17:54:39Z","2024-04-02T17:54:39Z"}]	{"010b18bf-96b9-499f-bb0f-7519a22ca870","publisher1","Publisher1","Account"}
"19afaa4e-e189-…	"ydcfowlsqtnow"	"Interactive Da…	"Easy web apps …	     "all"	              null	        null	        null	        null           	 null	         null	                 null	       null	          null	        null	       null	     null	         null	            null	                null	              null	"2024-04-02T17:…	  "2024-04-02T17:…	      "9"	 "python-shiny"	              ""	        false	     "Local"	      null	     null	  "3.11.6"	          null	                    null	                            null	                     true	                             null	  null	              false	"010b18bf-96b9-…	"https://wonder…	"https://wonder…	 "owner"	 "9"	  [{"7","Python","1","2024-04-02T17:52:08Z","2024-04-02T17:52:08Z"}, {"10","Shiny","7","2024-04-02T17:53:54Z","2024-04-02T17:53:54Z"}]	{"010b18bf-96b9-499f-bb0f-7519a22ca870","publisher1","Publisher1","Account"}

```

## R

```{r}
library(connectapi)

#### User-defined inputs ####
# 1. specify the username for the user of interest
username <- "SPECIFY USERNAME"
###########################

client <- connect()

# Get user's `guid` from specified username
user_guid <- user_guid_from_username(client, username)

# Get list of content owned by specified user
content <- get_content(client, owner_guid = user_guid)

```

### Example output

```
# A tibble: 3 × 45
  guid               name  title description access_type connection_timeout read_timeout init_timeout idle_timeout
  <chr>              <chr> <chr> <chr>       <chr>                    <int>        <int>        <int>        <int>
1 f55cdaed-c13e-483… cgrn… Lite… An open-so… all                         NA           NA           NA           NA
2 1c5278e5-a654-426… cjbx… Loan… An API ser… all                         NA           NA           NA           NA
3 19afaa4e-e189-49f… ydcf… Inte… Easy web a… all                         NA           NA           NA           NA
# ℹ 36 more variables: max_processes <int>, min_processes <int>, max_conns_per_process <int>, load_factor <dbl>,
#   memory_request <lgl>, memory_limit <lgl>, cpu_request <lgl>, cpu_limit <lgl>, amd_gpu_limit <lgl>,
#   nvidia_gpu_limit <lgl>, service_account_name <lgl>, default_image_name <lgl>, created_time <dttm>,
#   last_deployed_time <dttm>, bundle_id <chr>, app_mode <chr>, content_category <chr>, parameterized <lgl>,
#   cluster_name <chr>, image_name <chr>, r_version <chr>, py_version <chr>, quarto_version <chr>,
#   r_environment_management <lgl>, default_r_environment_management <lgl>, py_environment_management <lgl>,
#   default_py_environment_management <lgl>, run_as <chr>, run_as_current_user <lgl>, owner_guid <chr>, …
```

:::


### Summarize content in a table

The output above can be presented in a formatted table for easier readability. In the code below, only the following fields are used:

- `title`
- `last_deployed_time`
- `r_version`
- `py_version`
- `quarto_version`
- `access_type`
- `dashboard_url`

You may modify this code to add or remove other fields to suit your requirements.

::: {.panel-tabset group="language"}

## Python

```{python}
from great_tables import GT, style, loc, system_fonts, md


# Select and format the columns of interest

content_info = (
  content
  .select("title", "access_type", "last_deployed_time", "r_version", "py_version", "quarto_version", "dashboard_url")
  # format the urls TODO: this will be unnecessary when great_tables adds fmt_url. See https://github.com/posit-dev/great-tables/issues/80
  .with_columns(pl.col(["dashboard_url"]).map_elements(lambda x: f"<{x}>", return_dtype=pl.String))
)

# Create table
(
  GT(content_info)
  .tab_header(title="Content owned by " + username)
  .fmt_markdown(columns=["dashboard_url"])
  .tab_style(style=style.text(decorate="underline"),locations=loc.body(columns=["dashboard_url"]))
  .tab_spanner(
    label="Language",
    columns=["r_version", "py_version", "quarto_version"]
  )
  .tab_spanner(
    label="Access Info",
    columns=["access_type", "dashboard_url"]
  )
  .cols_move_to_end(columns=["access_type", "dashboard_url"])
)

```

### Example output

<div>
<div id="wzunztfnpm" style="padding-left:0px;padding-right:0px;padding-top:10px;padding-bottom:10px;overflow-x:auto;overflow-y:auto;width:auto;height:auto;">
<style>
#wzunztfnpm table {
          font-family: -apple-system, BlinkMacSystemFont, 'Segoe UI', Roboto, Oxygen, Ubuntu, Cantarell, 'Helvetica Neue', 'Fira Sans', 'Droid Sans', Arial, sans-serif;
          -webkit-font-smoothing: antialiased;
          -moz-osx-font-smoothing: grayscale;
        }

#wzunztfnpm thead, tbody, tfoot, tr, td, th { border-style: none; }
 tr { background-color: transparent; }
#wzunztfnpm p { margin: 0; padding: 0; }
 #wzunztfnpm .gt_table { display: table; border-collapse: collapse; line-height: normal; margin-left: auto; margin-right: auto; color: #333333; font-size: 16px; font-weight: normal; font-style: normal; background-color: #FFFFFF; width: auto; border-top-style: solid; border-top-width: 2px; border-top-color: #A8A8A8; border-right-style: none; border-right-width: 2px; border-right-color: #D3D3D3; border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #A8A8A8; border-left-style: none; border-left-width: 2px; border-left-color: #D3D3D3; }
 #wzunztfnpm .gt_caption { padding-top: 4px; padding-bottom: 4px; }
 #wzunztfnpm .gt_title { color: #333333; font-size: 125%; font-weight: initial; padding-top: 4px; padding-bottom: 4px; padding-left: 5px; padding-right: 5px; border-bottom-color: #FFFFFF; border-bottom-width: 0; }
 #wzunztfnpm .gt_subtitle { color: #333333; font-size: 85%; font-weight: initial; padding-top: 3px; padding-bottom: 5px; padding-left: 5px; padding-right: 5px; border-top-color: #FFFFFF; border-top-width: 0; }
 #wzunztfnpm .gt_heading { background-color: #FFFFFF; text-align: center; border-bottom-color: #FFFFFF; border-left-style: none; border-left-width: 1px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 1px; border-right-color: #D3D3D3; }
 #wzunztfnpm .gt_bottom_border { border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; }
 #wzunztfnpm .gt_col_headings { border-top-style: solid; border-top-width: 2px; border-top-color: #D3D3D3; border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; border-left-style: none; border-left-width: 1px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 1px; border-right-color: #D3D3D3; }
 #wzunztfnpm .gt_col_heading { color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: normal; text-transform: inherit; border-left-style: none; border-left-width: 1px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 1px; border-right-color: #D3D3D3; vertical-align: bottom; padding-top: 5px; padding-bottom: 5px; padding-left: 5px; padding-right: 5px; overflow-x: hidden; }
 #wzunztfnpm .gt_column_spanner_outer { color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: normal; text-transform: inherit; padding-top: 0; padding-bottom: 0; padding-left: 4px; padding-right: 4px; }
 #wzunztfnpm .gt_column_spanner_outer:first-child { padding-left: 0; }
 #wzunztfnpm .gt_column_spanner_outer:last-child { padding-right: 0; }
 #wzunztfnpm .gt_column_spanner { border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; vertical-align: bottom; padding-top: 5px; padding-bottom: 5px; overflow-x: hidden; display: inline-block; width: 100%; }
 #wzunztfnpm .gt_spanner_row { border-bottom-style: hidden; }
 #wzunztfnpm .gt_group_heading { padding-top: 8px; padding-bottom: 8px; padding-left: 5px; padding-right: 5px; color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: initial; text-transform: inherit; border-top-style: solid; border-top-width: 2px; border-top-color: #D3D3D3; border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; border-left-style: none; border-left-width: 1px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 1px; border-right-color: #D3D3D3; vertical-align: middle; text-align: left; }
 #wzunztfnpm .gt_empty_group_heading { padding: 0.5px; color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: initial; border-top-style: solid; border-top-width: 2px; border-top-color: #D3D3D3; border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; vertical-align: middle; }
 #wzunztfnpm .gt_from_md> :first-child { margin-top: 0; }
 #wzunztfnpm .gt_from_md> :last-child { margin-bottom: 0; }
 #wzunztfnpm .gt_row { padding-top: 8px; padding-bottom: 8px; padding-left: 5px; padding-right: 5px; margin: 10px; border-top-style: solid; border-top-width: 1px; border-top-color: #D3D3D3; border-left-style: none; border-left-width: 1px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 1px; border-right-color: #D3D3D3; vertical-align: middle; overflow-x: hidden; }
 #wzunztfnpm .gt_stub { color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: initial; text-transform: inherit; border-right-style: solid; border-right-width: 2px; border-right-color: #D3D3D3; padding-left: 5px; padding-right: 5px; }
 #wzunztfnpm .gt_stub_row_group { color: #333333; background-color: #FFFFFF; font-size: 100%; font-weight: initial; text-transform: inherit; border-right-style: solid; border-right-width: 2px; border-right-color: #D3D3D3; padding-left: 5px; padding-right: 5px; vertical-align: top; }
 #wzunztfnpm .gt_row_group_first td { border-top-width: 2px; }
 #wzunztfnpm .gt_row_group_first th { border-top-width: 2px; }
 #wzunztfnpm .gt_table_body { border-top-style: solid; border-top-width: 2px; border-top-color: #D3D3D3; border-bottom-style: solid; border-bottom-width: 2px; border-bottom-color: #D3D3D3; }
 #wzunztfnpm .gt_sourcenotes { color: #333333; background-color: #FFFFFF; border-bottom-style: none; border-bottom-width: 2px; border-bottom-color: #D3D3D3; border-left-style: none; border-left-width: 2px; border-left-color: #D3D3D3; border-right-style: none; border-right-width: 2px; border-right-color: #D3D3D3; }
 #wzunztfnpm .gt_sourcenote { font-size: 90%; padding-top: 4px; padding-bottom: 4px; padding-left: 5px; padding-right: 5px; text-align: left; }
 #wzunztfnpm .gt_left { text-align: left; }
 #wzunztfnpm .gt_center { text-align: center; }
 #wzunztfnpm .gt_right { text-align: right; font-variant-numeric: tabular-nums; }
 #wzunztfnpm .gt_font_normal { font-weight: normal; }
 #wzunztfnpm .gt_font_bold { font-weight: bold; }
 #wzunztfnpm .gt_font_italic { font-style: italic; }
 #wzunztfnpm .gt_super { font-size: 65%; }
 #wzunztfnpm .gt_footnote_marks { font-size: 75%; vertical-align: 0.4em; position: initial; }
 #wzunztfnpm .gt_asterisk { font-size: 100%; vertical-align: 0; }

</style>

<table class="gt_table table table-sm table-striped small" data-quarto-postprocess="true" data-quarto-disable-processing="false" data-quarto-bootstrap="false">
<thead class="gt_header">
<tr class="header">
<th colspan="7" class="gt_heading gt_title gt_font_normal" data-quarto-table-cell-role="th">Content owned by publisher1</th>
</tr>
</thead>
<tbody>
<tr class="odd gt_col_headings gt_spanner_row">
<td rowspan="2" id="title" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">title</td>
<td rowspan="2" id="last_deployed_time" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">last_deployed_time</td>
<td colspan="3" id="Language" class="gt_center gt_columns_top_border gt_column_spanner_outer" data-quarto-table-cell-role="th" scope="colgroup"><span class="gt_column_spanner">Language</span></td>
<td colspan="2" id="Access Info" class="gt_center gt_columns_top_border gt_column_spanner_outer" data-quarto-table-cell-role="th" scope="colgroup"><span class="gt_column_spanner">Access Info</span></td>
</tr>
<tr class="even gt_col_headings">
<td id="r_version" class="gt_col_heading gt_columns_bottom_border gt_center" data-quarto-table-cell-role="th" scope="col">r_version</td>
<td id="py_version" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">py_version</td>
<td id="quarto_version" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">quarto_version</td>
<td id="access_type" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">access_type</td>
<td id="dashboard_url" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">dashboard_url</td>
</tr>
</tbody>
<tbody class="gt_table_body">
<tr class="odd">
<td class="gt_row gt_left">Literate Programming with Quarto</td>
<td class="gt_row gt_left">2024-04-02T17:54:40Z</td>
<td class="gt_row gt_center">None</td>
<td class="gt_row gt_left">3.11.6</td>
<td class="gt_row gt_left">1.4.549</td>
<td class="gt_row gt_left">acl</td>
<td class="gt_row gt_left" style="text-decoration: underline"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee</a></td>
</tr>
<tr class="even">
<td class="gt_row gt_left">Loan Risk Prediction Model using FastAPI</td>
<td class="gt_row gt_left">2024-04-02T17:53:55Z</td>
<td class="gt_row gt_center">None</td>
<td class="gt_row gt_left">3.11.6</td>
<td class="gt_row gt_left">None</td>
<td class="gt_row gt_left">all</td>
<td class="gt_row gt_left" style="text-decoration: underline"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40</a></td>
</tr>
<tr class="odd">
<td class="gt_row gt_left">Interactive Data Exploration with Shiny for Python</td>
<td class="gt_row gt_left">2024-04-02T17:52:45Z</td>
<td class="gt_row gt_center">None</td>
<td class="gt_row gt_left">3.11.6</td>
<td class="gt_row gt_left">None</td>
<td class="gt_row gt_left">all</td>
<td class="gt_row gt_left" style="text-decoration: underline"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f</a></td>
</tr>
</tbody>
</table>


</div>

</div>

## R

```{r}
library(dplyr)
library(gt)

# Select and format the columns of interest in a table
content |>
  select("title", "description", "access_type", "created_time", "last_deployed_time", "bundle_id", "app_mode", "content_category", "r_version", "py_version", "quarto_version", "content_url", "dashboard_url") |>
  gt() |>
  tab_header(title = paste("Content owned by",username)) |>
  fmt_url(columns = c(content_url, dashboard_url)) |>
  tab_spanner(label="Deployment Info",
              columns=c(created_time, last_deployed_time))
```

### Example output

<div>
<div id="tithrumycv" style="padding-left:0px;padding-right:0px;padding-top:10px;padding-bottom:10px;overflow-x:auto;overflow-y:auto;width:auto;height:auto;">
<style>#tithrumycv table {
  font-family: system-ui, 'Segoe UI', Roboto, Helvetica, Arial, sans-serif, 'Apple Color Emoji', 'Segoe UI Emoji', 'Segoe UI Symbol', 'Noto Color Emoji';
  -webkit-font-smoothing: antialiased;
  -moz-osx-font-smoothing: grayscale;
}

#tithrumycv thead, #tithrumycv tbody, #tithrumycv tfoot, #tithrumycv tr, #tithrumycv td, #tithrumycv th {
  border-style: none;
}

#tithrumycv p {
  margin: 0;
  padding: 0;
}

#tithrumycv .gt_table {
  display: table;
  border-collapse: collapse;
  line-height: normal;
  margin-left: auto;
  margin-right: auto;
  color: #333333;
  font-size: 16px;
  font-weight: normal;
  font-style: normal;
  background-color: #FFFFFF;
  width: auto;
  border-top-style: solid;
  border-top-width: 2px;
  border-top-color: #A8A8A8;
  border-right-style: none;
  border-right-width: 2px;
  border-right-color: #D3D3D3;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #A8A8A8;
  border-left-style: none;
  border-left-width: 2px;
  border-left-color: #D3D3D3;
}

#tithrumycv .gt_caption {
  padding-top: 4px;
  padding-bottom: 4px;
}

#tithrumycv .gt_title {
  color: #333333;
  font-size: 125%;
  font-weight: initial;
  padding-top: 4px;
  padding-bottom: 4px;
  padding-left: 5px;
  padding-right: 5px;
  border-bottom-color: #FFFFFF;
  border-bottom-width: 0;
}

#tithrumycv .gt_subtitle {
  color: #333333;
  font-size: 85%;
  font-weight: initial;
  padding-top: 3px;
  padding-bottom: 5px;
  padding-left: 5px;
  padding-right: 5px;
  border-top-color: #FFFFFF;
  border-top-width: 0;
}

#tithrumycv .gt_heading {
  background-color: #FFFFFF;
  text-align: center;
  border-bottom-color: #FFFFFF;
  border-left-style: none;
  border-left-width: 1px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 1px;
  border-right-color: #D3D3D3;
}

#tithrumycv .gt_bottom_border {
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
}

#tithrumycv .gt_col_headings {
  border-top-style: solid;
  border-top-width: 2px;
  border-top-color: #D3D3D3;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  border-left-style: none;
  border-left-width: 1px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 1px;
  border-right-color: #D3D3D3;
}

#tithrumycv .gt_col_heading {
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: normal;
  text-transform: inherit;
  border-left-style: none;
  border-left-width: 1px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 1px;
  border-right-color: #D3D3D3;
  vertical-align: bottom;
  padding-top: 5px;
  padding-bottom: 6px;
  padding-left: 5px;
  padding-right: 5px;
  overflow-x: hidden;
}

#tithrumycv .gt_column_spanner_outer {
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: normal;
  text-transform: inherit;
  padding-top: 0;
  padding-bottom: 0;
  padding-left: 4px;
  padding-right: 4px;
}

#tithrumycv .gt_column_spanner_outer:first-child {
  padding-left: 0;
}

#tithrumycv .gt_column_spanner_outer:last-child {
  padding-right: 0;
}

#tithrumycv .gt_column_spanner {
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  vertical-align: bottom;
  padding-top: 5px;
  padding-bottom: 5px;
  overflow-x: hidden;
  display: inline-block;
  width: 100%;
}

#tithrumycv .gt_spanner_row {
  border-bottom-style: hidden;
}

#tithrumycv .gt_group_heading {
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: initial;
  text-transform: inherit;
  border-top-style: solid;
  border-top-width: 2px;
  border-top-color: #D3D3D3;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  border-left-style: none;
  border-left-width: 1px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 1px;
  border-right-color: #D3D3D3;
  vertical-align: middle;
  text-align: left;
}

#tithrumycv .gt_empty_group_heading {
  padding: 0.5px;
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: initial;
  border-top-style: solid;
  border-top-width: 2px;
  border-top-color: #D3D3D3;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  vertical-align: middle;
}

#tithrumycv .gt_from_md > :first-child {
  margin-top: 0;
}

#tithrumycv .gt_from_md > :last-child {
  margin-bottom: 0;
}

#tithrumycv .gt_row {
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
  margin: 10px;
  border-top-style: solid;
  border-top-width: 1px;
  border-top-color: #D3D3D3;
  border-left-style: none;
  border-left-width: 1px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 1px;
  border-right-color: #D3D3D3;
  vertical-align: middle;
  overflow-x: hidden;
}

#tithrumycv .gt_stub {
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: initial;
  text-transform: inherit;
  border-right-style: solid;
  border-right-width: 2px;
  border-right-color: #D3D3D3;
  padding-left: 5px;
  padding-right: 5px;
}

#tithrumycv .gt_stub_row_group {
  color: #333333;
  background-color: #FFFFFF;
  font-size: 100%;
  font-weight: initial;
  text-transform: inherit;
  border-right-style: solid;
  border-right-width: 2px;
  border-right-color: #D3D3D3;
  padding-left: 5px;
  padding-right: 5px;
  vertical-align: top;
}

#tithrumycv .gt_row_group_first td {
  border-top-width: 2px;
}

#tithrumycv .gt_row_group_first th {
  border-top-width: 2px;
}

#tithrumycv .gt_summary_row {
  color: #333333;
  background-color: #FFFFFF;
  text-transform: inherit;
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
}

#tithrumycv .gt_first_summary_row {
  border-top-style: solid;
  border-top-color: #D3D3D3;
}

#tithrumycv .gt_first_summary_row.thick {
  border-top-width: 2px;
}

#tithrumycv .gt_last_summary_row {
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
}

#tithrumycv .gt_grand_summary_row {
  color: #333333;
  background-color: #FFFFFF;
  text-transform: inherit;
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
}

#tithrumycv .gt_first_grand_summary_row {
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
  border-top-style: double;
  border-top-width: 6px;
  border-top-color: #D3D3D3;
}

#tithrumycv .gt_last_grand_summary_row_top {
  padding-top: 8px;
  padding-bottom: 8px;
  padding-left: 5px;
  padding-right: 5px;
  border-bottom-style: double;
  border-bottom-width: 6px;
  border-bottom-color: #D3D3D3;
}

#tithrumycv .gt_striped {
  background-color: rgba(128, 128, 128, 0.05);
}

#tithrumycv .gt_table_body {
  border-top-style: solid;
  border-top-width: 2px;
  border-top-color: #D3D3D3;
  border-bottom-style: solid;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
}

#tithrumycv .gt_footnotes {
  color: #333333;
  background-color: #FFFFFF;
  border-bottom-style: none;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  border-left-style: none;
  border-left-width: 2px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 2px;
  border-right-color: #D3D3D3;
}

#tithrumycv .gt_footnote {
  margin: 0px;
  font-size: 90%;
  padding-top: 4px;
  padding-bottom: 4px;
  padding-left: 5px;
  padding-right: 5px;
}

#tithrumycv .gt_sourcenotes {
  color: #333333;
  background-color: #FFFFFF;
  border-bottom-style: none;
  border-bottom-width: 2px;
  border-bottom-color: #D3D3D3;
  border-left-style: none;
  border-left-width: 2px;
  border-left-color: #D3D3D3;
  border-right-style: none;
  border-right-width: 2px;
  border-right-color: #D3D3D3;
}

#tithrumycv .gt_sourcenote {
  font-size: 90%;
  padding-top: 4px;
  padding-bottom: 4px;
  padding-left: 5px;
  padding-right: 5px;
}

#tithrumycv .gt_left {
  text-align: left;
}

#tithrumycv .gt_center {
  text-align: center;
}

#tithrumycv .gt_right {
  text-align: right;
  font-variant-numeric: tabular-nums;
}

#tithrumycv .gt_font_normal {
  font-weight: normal;
}

#tithrumycv .gt_font_bold {
  font-weight: bold;
}

#tithrumycv .gt_font_italic {
  font-style: italic;
}

#tithrumycv .gt_super {
  font-size: 65%;
}

#tithrumycv .gt_footnote_marks {
  font-size: 75%;
  vertical-align: 0.4em;
  position: initial;
}

#tithrumycv .gt_asterisk {
  font-size: 100%;
  vertical-align: 0;
}

#tithrumycv .gt_indent_1 {
  text-indent: 5px;
}

#tithrumycv .gt_indent_2 {
  text-indent: 10px;
}

#tithrumycv .gt_indent_3 {
  text-indent: 15px;
}

#tithrumycv .gt_indent_4 {
  text-indent: 20px;
}

#tithrumycv .gt_indent_5 {
  text-indent: 25px;
}
</style>

<table class="gt_table table table-sm table-striped small" data-quarto-postprocess="true" data-quarto-disable-processing="false" data-quarto-bootstrap="false">
<thead>
<tr class="header gt_heading">
<th colspan="7" class="gt_heading gt_title gt_font_normal gt_bottom_border">Content owned by publisher1</th>
</tr>
<tr class="odd gt_col_headings gt_spanner_row">
<th rowspan="2" id="title" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">title</th>
<th rowspan="2" id="last_deployed_time" class="gt_col_heading gt_columns_bottom_border gt_right" data-quarto-table-cell-role="th" scope="col">last_deployed_time</th>
<th colspan="3" id="Language" class="gt_center gt_columns_top_border gt_column_spanner_outer" data-quarto-table-cell-role="th" scope="colgroup"><span class="gt_column_spanner">Language</span></th>
<th colspan="2" id="Access Info" class="gt_center gt_columns_top_border gt_column_spanner_outer" data-quarto-table-cell-role="th" scope="colgroup"><span class="gt_column_spanner">Access Info</span></th>
</tr>
<tr class="header gt_col_headings">
<th id="r_version" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">r_version</th>
<th id="py_version" class="gt_col_heading gt_columns_bottom_border gt_right" data-quarto-table-cell-role="th" scope="col">py_version</th>
<th id="quarto_version" class="gt_col_heading gt_columns_bottom_border gt_right" data-quarto-table-cell-role="th" scope="col">quarto_version</th>
<th id="access_type" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">access_type</th>
<th id="dashboard_url" class="gt_col_heading gt_columns_bottom_border gt_left" data-quarto-table-cell-role="th" scope="col">dashboard_url</th>
</tr>
</thead>
<tbody class="gt_table_body">
<tr class="odd">
<td class="gt_row gt_left" headers="title">Literate Programming with Quarto</td>
<td class="gt_row gt_right" headers="last_deployed_time">2024-04-02 17:54:40</td>
<td class="gt_row gt_left" headers="r_version">NA</td>
<td class="gt_row gt_right" headers="py_version">3.11.6</td>
<td class="gt_row gt_right" headers="quarto_version">1.4.549</td>
<td class="gt_row gt_left" headers="access_type">acl</td>
<td class="gt_row gt_left" headers="dashboard_url"><span style="white-space: pre;"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee" target="_blank" style="color:#008B8B;text-decoration:underline;text-underline-position: under;display: inline-block;" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/f55cdaed-c13e-4838-b466-c288e021f5ee</a></span></td>
</tr>
<tr class="even">
<td class="gt_row gt_left" headers="title">Loan Risk Prediction Model using FastAPI</td>
<td class="gt_row gt_right" headers="last_deployed_time">2024-04-02 17:53:55</td>
<td class="gt_row gt_left" headers="r_version">NA</td>
<td class="gt_row gt_right" headers="py_version">3.11.6</td>
<td class="gt_row gt_right" headers="quarto_version">NA</td>
<td class="gt_row gt_left" headers="access_type">all</td>
<td class="gt_row gt_left" headers="dashboard_url"><span style="white-space: pre;"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40" target="_blank" style="color:#008B8B;text-decoration:underline;text-underline-position: under;display: inline-block;" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/1c5278e5-a654-4267-9a51-b06992db1b40</a></span></td>
</tr>
<tr class="odd">
<td class="gt_row gt_left" headers="title">Interactive Data Exploration with Shiny for Python</td>
<td class="gt_row gt_right" headers="last_deployed_time">2024-04-02 17:52:45</td>
<td class="gt_row gt_left" headers="r_version">NA</td>
<td class="gt_row gt_right" headers="py_version">3.11.6</td>
<td class="gt_row gt_right" headers="quarto_version">NA</td>
<td class="gt_row gt_left" headers="access_type">all</td>
<td class="gt_row gt_left" headers="dashboard_url"><span style="white-space: pre;"><a href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f" target="_blank" style="color:#008B8B;text-decoration:underline;text-underline-position: under;display: inline-block;" data-original-href="https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f">https://spotted-caribou.staging.eval.posit.co/pub/connect/#/apps/19afaa4e-e189-49f4-bcd3-c5aa094b362f</a></span></td>
</tr>
</tbody>
</table>

</div>
</div>

:::
